---
title: "ShinyStan Automated Estimates Report"
output:
  html_document: 
    toc: TRUE
    toc_float: 
      collapsed: FALSE
      depth: 3
  pdf_document: 
    toc: TRUE
  word_document: 
    toc: TRUE
date: "`r format(Sys.time(), '%d %B %Y, %H:%M')`"
fontsize: 11pt
---


```{r global_options, include=FALSE}
# Within the function generate_report the shinystan object (sso) is prepared for this markdown file.
# The following can be used to prepare the sso for use with this markdown file.
# nopars is a logical value that describes if the pars argument has been used.
#
# if(nopars){
#   selected_parameters <- sso@param_names[order(sso@summary[, "n_eff"])] 
#   selected_parameters <- selected_parameters[-which(selected_parameters == "log-posterior")]
#   
#   if(n_param == "all") n_param <- length(selected_parameters)
#   if(n_param > length(selected_parameters)) n_param <- length(selected_parameters)
#   sso <- drop_parameters(sso, pars = selected_parameters[-c(1:n_param)])
# } else {
#   selected_parameters <- sso@param_names[order(sso@summary[, "n_eff"])] 
#   selected_parameters <- selected_parameters[-which(selected_parameters == "log-posterior")]
#   selected_parameters <- c(pars, selected_parameters[-which(selected_parameters %in% pars)])
#   n_param <- length(pars)
#   sso <- drop_parameters(sso, pars = selected_parameters[-which(selected_parameters %in% pars)])
# }
# 
library(dplyr)
library(bayesplot)

knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, comment = "  ")
showplots <- FALSE

printf <- function(msg = "%5.3f", ...) {
  cat(sprintf(msg, ...))
}


# To make listed parameter overviews
.make_param_list <- function(object) {
  param_names <- slot(object, "param_names")
  param_dims <- slot(object, "param_dims")
  param_groups <- names(param_dims)
  choices <- list()
  ll <- length(param_dims)
  choices[seq_len(ll)] <- ""
  names(choices) <- param_groups
  for(i in seq_len(ll)) {
    if (length(param_dims[[i]]) == 0) {
      choices[[i]] <- list(param_groups[i])
    }
    else {
      temp <- paste0(param_groups[i],"\\[")
      choices[[i]] <- param_names[grep(temp, param_names)]
    }
  }
  choices
}


.make_param_list_with_groups <- function(object, sort_j = FALSE) {
  param_names <- slot(object, "param_names")
  param_dims <- slot(object, "param_dims")
  param_groups <- names(param_dims)
  ll <- length(param_dims)
  LL <- sapply(seq_len(ll), function(i) length(param_dims[[i]]))
  choices <- list()
  choices[seq_len(ll)] <- ""
  names(choices) <- param_groups
  for(i in seq_len(ll)) {
    if (LL[i] == 0) {
      choices[[i]] <- list(param_groups[i])
    } else {
      group <- param_groups[i]
      temp <- paste0("^",group,"\\[")
      ch <- param_names[grep(temp, param_names)]
      
      #       toggle row/column major sorting so e.g. "beta[1,1], beta[1,2],
      #       beta[2,1], beta[2,2]" instead of "beta[1,1], beta[2,1], beta[1,2],
      #       beta[2,2]"
      if (sort_j == TRUE & LL[i] > 1)
        ch <- gtools::mixedsort(ch)
      
      ch_out <- c(paste0(group,"_as_shinystan_group"), ch)
      names(ch_out) <- c(paste("ALL (remaining)", group), ch)
      choices[[i]] <- ch_out
    }
  }
  
  choices
}


```

# Warnings

```{r}

divergences <- sum(nuts_params(sso@sampler_params %>%
                                 lapply(., as.data.frame) %>%
                                 lapply(., filter, row_number() > sso@n_warmup) %>%
                                 lapply(., as.matrix), 
                               pars = "divergent__")[, 3]) != 0



if(divergences) {
  lapply(sso@sampler_params, "[", , "divergent__") %>%
    lapply(., as.data.frame) %>%
    lapply(., filter, row_number() > sso@n_warmup) %>%
    lapply(., function (x) x > 0 ) %>% lapply(., sum) %>% 
    unlist(.) %>% sum(.) %>%
    paste0(., " of ", (sso@n_iter-sso@n_warmup) * sso@n_chain,
           " iterations ended with a divergence (",
           round((. / ((sso@n_iter-sso@n_warmup) * sso@n_chain)) * 100, 1),
           "%).")
} else {
  print(paste0("None of the ", (sso@n_iter-sso@n_warmup) * sso@n_chain, 
               " iterations ended with a divergent transition."))
}



```

\newpage

# Visual Estimates

## Density

These are density plots of `r if(nopars == FALSE){selected_parameters}``r if(nopars){paste0("the ", n_param, " worst performing parameters in terms of n_eff")}`.

```{r density_plots, out.width = '45%', fig.show = 'hold'}
for(i in 1:n_param) {
  print(mcmc_dens(
    sso@posterior_sample[(1 + sso@n_warmup) : sso@n_iter, , ],
    pars = selected_parameters[i]
  ))
}
``` 

\newpage

## Histogram

These are histogram plots `r if(nopars == FALSE){selected_parameters}``r if(nopars){paste0("the ", n_param, " worst performing parameters in terms of n_eff")}`.

```{r histogram_plots, out.width = '45%', fig.show = 'hold'}
for(i in 1:n_param) {
  print(mcmc_hist(
    sso@posterior_sample[(1 + sso@n_warmup) : sso@n_iter, , ],
    pars = selected_parameters[i]
  ))
}
``` 


\newpage

## Interval


These are interval plots of `r if(nopars == FALSE){selected_parameters}``r if(nopars){paste0("the ", n_param, " worst performing parameters in terms of n_eff")}`. The plots are split by parameter groups. The entire group is printed if one of the parameters is included in the worst performing parameters. The point represents median value, the inner edge the 50\% CI and the outer the 95\% CI. 

```{r interval_plots, out.width = '45%', fig.show = 'hold'}

for(i in 1:length(.make_param_list_with_groups(sso))){
  if(any(.make_param_list_with_groups(sso)[[i]] %in% selected_parameters)){
    parameters <- as.character(.make_param_list_with_groups(sso)[[i]][.make_param_list_with_groups(sso)[[i]] %in% sso@param_names])
    print(mcmc_intervals(
      sso@posterior_sample[(1 + sso@n_warmup) : sso@n_iter, , ],
      pars = parameters,
      point_est = "median",
      prob = .50,
      prob_outer = .95
    ))
  }
}

``` 

\newpage

## Areas


These are areas plots of `r if(nopars == FALSE){selected_parameters}``r if(nopars){paste0("the ", n_param, " worst performing parameters in terms of n_eff")}`. The plots are split by parameter groups. The entire group is printed if one of the parameters is included in the worst performing parameters. The point represents median value, the inner edge the 50\% CI and the outer the 95\% CI. 

```{r areas_plots, out.width = '45%', fig.show = 'hold'}

for(i in 1:length(.make_param_list_with_groups(sso))){
  if(any(.make_param_list_with_groups(sso)[[i]] %in% selected_parameters)){
    parameters <- as.character(.make_param_list_with_groups(sso)[[i]][.make_param_list_with_groups(sso)[[i]] %in% sso@param_names])
    print(mcmc_areas(
      sso@posterior_sample[(1 + sso@n_warmup) : sso@n_iter, , ],
      pars = parameters,
      point_est = "median",
      prob = .50,
      prob_outer = .95
    ))
  }
}

``` 


\newpage

# Model Code

```{r model_code}
if(object.size(sso@model_code) < 8000){
  printf(sso@model_code)
} else {
  print(sso@model_code)
}
```