---
title: "ShinyStan Automated Estimates Report"
output:
  html_document: 
    toc: TRUE
    toc_float: 
      collapsed: FALSE
      depth: 3
  pdf_document: 
    toc: TRUE
  word_document: 
    toc: TRUE
date: "`r format(Sys.time(), '%d %B %Y, %H:%M')`"
fontsize: 11pt
---


```{r global_options, include=FALSE}
library(dplyr)
library(bayesplot)

knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, comment = "  ")
showplots <- FALSE

printf <- function(msg = "%5.3f", ...) {
  cat(sprintf(msg, ...))
}


# To make listed parameter overviews
.make_param_list <- function(object) {
  param_names <- slot(object, "param_names")
  param_dims <- slot(object, "param_dims")
  param_groups <- names(param_dims)
  choices <- list()
  ll <- length(param_dims)
  choices[seq_len(ll)] <- ""
  names(choices) <- param_groups
  for(i in seq_len(ll)) {
    if (length(param_dims[[i]]) == 0) {
      choices[[i]] <- list(param_groups[i])
    }
    else {
      temp <- paste0(param_groups[i],"\\[")
      choices[[i]] <- param_names[grep(temp, param_names)]
    }
  }
  choices
}


.make_param_list_with_groups <- function(object, sort_j = FALSE) {
  param_names <- slot(object, "param_names")
  param_dims <- slot(object, "param_dims")
  param_groups <- names(param_dims)
  ll <- length(param_dims)
  LL <- sapply(seq_len(ll), function(i) length(param_dims[[i]]))
  choices <- list()
  choices[seq_len(ll)] <- ""
  names(choices) <- param_groups
  for(i in seq_len(ll)) {
    if (LL[i] == 0) {
      choices[[i]] <- list(param_groups[i])
    } else {
      group <- param_groups[i]
      temp <- paste0("^",group,"\\[")
      ch <- param_names[grep(temp, param_names)]
      
      #       toggle row/column major sorting so e.g. "beta[1,1], beta[1,2],
      #       beta[2,1], beta[2,2]" instead of "beta[1,1], beta[2,1], beta[1,2],
      #       beta[2,2]"
      if (sort_j == TRUE & LL[i] > 1)
        ch <- gtools::mixedsort(ch)
      
      ch_out <- c(paste0(group,"_as_shinystan_group"), ch)
      names(ch_out) <- c(paste("ALL (remaining)", group), ch)
      choices[[i]] <- ch_out
    }
  }
  
  choices
}


nopars <- missing(pars) | is.null(pars)

if(nopars){
  selected_parameters <- order(sso@summary[, "n_eff"]) %>%
    sso@param_names[.] 
  
  if(n_param == "all") n_param <- length(selected_parameters)
  if(n_param > length(selected_parameters)) n_param <- length(selected_parameters)
} else {
  selected_parameters <- pars
  n_param <- length(pars)
}


```

# Visual Estimates

## Density

These are density plots of `r if(nopars == FALSE){selected_parameters}``r if(nopars){paste0("the ", n_param, " worst performing parameters in terms of n_eff")}`.

```{r density_plots, out.width = '45%', fig.show = 'hold'}
for(i in 1:n_param) {
  print(mcmc_dens(
    sso@posterior_sample[(1 + sso@n_warmup) : sso@n_iter, , ],
    pars = selected_parameters[i]
  ))
}
``` 

\newpage

## Histogram

These are histogram plots `r if(nopars == FALSE){selected_parameters}``r if(nopars){paste0("the ", n_param, " worst performing parameters in terms of n_eff")}`.

```{r histogram_plots, out.width = '45%', fig.show = 'hold'}
for(i in 1:n_param) {
  print(mcmc_hist(
    sso@posterior_sample[(1 + sso@n_warmup) : sso@n_iter, , ],
    pars = selected_parameters[i]
  ))
}
``` 


\newpage

## Interval


These are interval plots of `r if(nopars == FALSE){selected_parameters}``r if(nopars){paste0("the ", n_param, " worst performing parameters in terms of n_eff")}`. The plots are split by parameter groups. The entire group is printed if one of the parameters is included in the worst performing parameters. The point represents median value, the inner edge the 50\% CI and the outer the 95\% CI. 

```{r interval_plots, out.width = '45%', fig.show = 'hold'}

for(i in 1:length(.make_param_list_with_groups(sso))){
  if(any(.make_param_list_with_groups(sso)[[i]] %in% selected_parameters)){
    parameters <- as.character(.make_param_list_with_groups(sso)[[i]][.make_param_list_with_groups(sso)[[i]] %in% sso@param_names])
    print(mcmc_intervals(
      sso@posterior_sample[(1 + sso@n_warmup) : sso@n_iter, , ],
      pars = parameters,
      point_est = "median",
      prob = .50,
      prob_outer = .95
    ))
  }
}

``` 

\newpage

## Areas


These are areas plots of `r if(nopars == FALSE){selected_parameters}``r if(nopars){paste0("the ", n_param, " worst performing parameters in terms of n_eff")}`. The plots are split by parameter groups. The entire group is printed if one of the parameters is included in the worst performing parameters. The point represents median value, the inner edge the 50\% CI and the outer the 95\% CI. 

```{r areas_plots, out.width = '45%', fig.show = 'hold'}

for(i in 1:length(.make_param_list_with_groups(sso))){
  if(any(.make_param_list_with_groups(sso)[[i]] %in% selected_parameters)){
    parameters <- as.character(.make_param_list_with_groups(sso)[[i]][.make_param_list_with_groups(sso)[[i]] %in% sso@param_names])
    print(mcmc_areas(
      sso@posterior_sample[(1 + sso@n_warmup) : sso@n_iter, , ],
      pars = parameters,
      point_est = "median",
      prob = .50,
      prob_outer = .95
    ))
  }
}

``` 


